Succinct representations for abstract interpretation

### 2011-11-01 papers/PLDI2012/implicitization.tex
commentaires resultats

Let us briefly comment the results given in more details in Table~\ref{tab:techniques} and Figure~\ref{fig:techniques}.
\emph{Guided Static Analysis} from \citet{DBLP:conf/sas/GopanR07} improves the
result of the classical Abstract Interpretation in $2.33\%$ of the control points
in $P_R$.
\emph{Path-focusing} from \citet{Monniaux_Gonnord_SAS11} gives
statistically better results, and finds better invariants than \emph{Guided
Static Analysis} in $8.58\%$ of the cases. However, it also loses precision in an
important number ($2.87\%$) of control points.
Finally, our combined technique gives the most promising results, since it is
statistically more precise than the other techniques.

\JH{Paragraphe a reecrire:}
The analysis using disjunctive invariants seems not to be as efficient as
expected, and often finds greater invariants than the combined technique
($11.64\%$). It probably means that our heuristic for the construction of
$\sigma$ is not effective enough. Usually, disjunctive invariants computation
finds precise loop invariants because they allow to distinguish for
instance the first loop iterations. In our case, such benefits are not
visible, since we have already unrolled every loops once.

>>>>

Let us briefly comment the results given in more details in Table~\ref{tab:techniques} and Figure~\ref{fig:techniques}.
\emph{Guided Static Analysis} from \citet{DBLP:conf/sas/GopanR07} improves the
result of the classical Abstract Interpretation in $2.72\%$ of the control points
in $P_R$.
\emph{Path-focusing} from \citet{Monniaux_Gonnord_SAS11} gives
statistically better results, and finds better invariants than \emph{Guided
Static Analysis} in $9.89\%$ of the cases. However, it also loses precision in an
important number ($2.68\%$) of control points.
Finally, our combined technique gives the most promising results, since it is
statistically more precise than the other techniques.

The analysis using disjunctive invariants greatly improves the
precision of the analysis (for $12.06\%$ of the control points in $P_R$), at an
acceptable time cost (see Table \ref{tab:time}).
